Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-21 paper.tex
intro cloud

%\noindent

>>>>

Many cloud vendors have started offering VM with GPUs in order to provide

Accelerators such as GPUs have been adopted by major cloud vendors,

as GPUs provide orders-of-magnitude speedup for computation-intensive data-parallel applications.

In cloud environments, sharing GPU resources among multiple virtual machines (VMs) is not straightforward which is translated into a low utilization rate.

accelerate general-purpose workloads in many applica-
tion domains such as supercomputing systems. Unfor-
tunately, enterprise and cloud computing domains have

inefficient access to GPU virtualization technology be-
cause the required resource isolation of multiple vir-
tual machines (VMs) accessing the same set of GPU re-
sources cannot be efficiently guaranteed.

Efficiently utilizing GPU resources in the cloud envi-
ronment is not so straightforward. Current commercial

cloud providers (e.g., Amazon Elastic Compute Cloud—

EC2) dedicate an individual physical instance of GPUs

to a VM, which causes resource under-utilization. A fea-
sible solution to make GPU a truly shared and schedula-
ble resource in the cloud is through GPU virtualization,

which allows multiple VMs to access the same set of

GPUs simultaneously. Recent research [8, 9, 14, 20, 26,

27] implements several GPU virtualization technologies

for graphics rendering applications as well as GPGPU

computing workloads.
